---
title: "CartographiesFBADS"
author: "André K. Rodarte"
date: "2023-08-22"
output: html_document
---

```{r setup, include=FALSE}
### References ####
#RadLibrary: https://github.com/facebookresearch/Radlibrary
#devtools::install_github("facebookresearch/Radlibrary")
#remotes::install_github("favstats/metatargetr")

library(tidyverse)
library(tidytext)
library(dplyr)
library(janitor)
library(highcharter)
library(httr)
library(furrr)
library(remotes)
library(lubridate)
library(purrr)
library(data.table)
library(stringdist)

#DATA VISUALIZATION
#install.packages('maps')
#install.packages("tibble")
#install.packages("forcats")
#install.packages("plotly")
#install.packages("sf")
library(ggplot2)
library(plotly)
library(sf)
library(maps)
library(tibble)
library(forcats)

#Regression analysis
#install.packages("caret")
#install.packages("car")
#install.packages("leaps")
#install.packages("MASS")
#install.packages("partykit")
#install.packages("nnet")
#install.packages("EMT")
library(caret)
library(car)
library(leaps)
library(MASS)
library(partykit)
library(nnet)
library(EMT)

#################################
###########FUNCTIONS#############
#################################
get_mid <- function(spend_upper_bound, spend_lower_bound) {
  # (spend_upper_bound-spend_lower_bound)/2+spend_lower_bound
  (spend_upper_bound+spend_lower_bound)/2
}

assign_colors <- function(dat, n = 12) {
  
  color_sample <- colorspace::divergingx_hcl(n)
  
  lenght <- dat$color[is.na(dat$color)] %>% length
  
  if(lenght==0) return(invisible())
  
  cols <- sample(color_sample, lenght, replace = T)
  
  dat$color[is.na(dat$color)] <- cols
  
  return(dat)
  
}
```

#Set up API Credentials

```{r setup, include=FALSE}
#################################
#################################
# Set up API credentials
access_token <- "E"

# Define the API endpoint URL
api_base_url <- "https://graph.facebook.com"
api_version <- "v15.0"  # Replace if necessary
endpoint <- file.path(api_base_url, api_version, "ads_archive")
#################################
#################################
```

#Query

```{r}
# First, save all of the data types that we will ask the API to extract.
fields_vector <- c("ad_data", "region_data", "demographic_data")

# Correspondingly, save all of the table types.
table_type_vector <- c("ad", "region", "demographic")

# Initiate an empty list to which we will append the extracted API data.
# The list could be initiated simply by using list(); however, especially for
# larger data sets, specifying the length of a list in R in advance speeds up
# the processing. The length of the list equals our 3 data types.
fb_ad_list <- vector(mode = "list", length = length(fields_vector))

# We will also name its three items with values from table_type_vector so we can
# refer to them further
names(fb_ad_list) <- table_type_vector

for (i in seq_along(fields_vector)) {
  print(paste("Extracting the", fields_vector[i]))
  
  query3 <- adlib_build_query(
    ad_reached_countries = "BR",
    ad_active_status = "ALL",
    search_terms = "Minas Gerais",
    #search_page_ids =
    ad_delivery_date_min = "2022-01-01",
    ad_delivery_date_max = "2022-10-10",
    ad_type = "POLITICAL_AND_ISSUE_ADS",
    publisher_platform = c(
      "FACEBOOK",
      "INSTAGRAM",
      "MESSENGER",
      "WHATSAPP"
    ),
    fields = fields_vector[i]
  )
  
  # The call is limited to 1000 results but pagination of overcomes it.
  # We pipe the output of the paginated call to the as_tibble function.
  fb_ad_list[[table_type_vector[i]]] <- adlib_get_paginated(query3,
                                                            token = access_token
  ) %>%
    as_tibble(
      type = table_type_vector[i],
      censor_access_token = TRUE
    )
}
```

#Summary of Ads (to complement RQ1)

```{r, warning=FALSE}
#Write dataset
df_terms <- fb_ad_list[["ad"]] %>%
  distinct() %>%
  arrange(desc(ad_creation_time))

#Combine by name
df_ads <- df_terms %>%
  group_by(page_name) %>%
  summarise(
    id = first(id),
    nr_ads = n(),
    spend_upper_sum = sum(spend_upper, na.rm = TRUE),
    spend_lower_sum = sum(spend_lower, na.rm = TRUE),
    impressions_upper_avg = mean(impressions_upper, na.rm = TRUE),
    #avg_prop_female_25_34 = mean(`female_25-34`, na.rm = TRUE),
    #avg_prop_male_25_34 = mean(`male_25-34`, na.rm = TRUE),
  ) %>%
  filter(nr_ads > 1) %>%
  arrange(desc(nr_ads)) %>% 
  mutate(mid_spent = get_mid(spend_upper_sum, spend_lower_sum))

head(df_ads, 20)
```

**Add accounts that promoted ads but could not be found in Crowdtangle**

```{r}
## Standardize the case (converting to lowercase)
## Remove leading and trailing white spaces
df$page_name <- trimws(df$page_name)
df$name_ballot <- trimws(df$name_ballot)
df_ads$page_name <- trimws(df_ads$page_name)


df$page_name <- tolower(df$page_name)
df$name_ballot <- tolower(df$name_ballot)
df_ads$page_name <- tolower(df_ads$page_name)

df$page_name = stri_trans_general(str = df$page_name, id = "Latin-ASCII")
df_ads$page_name = stri_trans_general(str = df_ads$page_name, id = "Latin-ASCII")

# Define a threshold for Levenshtein distance to consider as a match
threshold <- 0.1

# Find approximate matches between "page_name" and "name_ballot" and store similarity information
similarity_info <- data.frame()
for (i in 1:nrow(df_ads)) {
  page_name <- df_ads$page_name[i]
  matches <- stringdist::amatch(page_name, df$name_ballot, method = "lv")
  filtered_matches <- matches[stringdist::stringdistmatrix(page_name, df$name_ballot[matches], method = "lv") <= threshold]
  
  if (length(filtered_matches) > 0) {
    match_info <- data.frame(page_name = page_name, name_ballot = df$name_ballot[filtered_matches], similarity = threshold - stringdist::stringdist(page_name, df$name_ballot[filtered_matches], method = "lv"))
    similarity_info <- rbind(similarity_info, match_info)
  }
}

# Print the resulting dataset with similarity information
df_similarity <- na.omit(similarity_info)

#Check for different accounts
differences_df <- setdiff(df$page_name, df_similarity$page_name)
differences_df_clean <- setdiff(df_similarity$page_name, df$page_name)

df_differences_df <- data.frame(page_name = differences_df, Indicator = "Only in df")
df_differences_df_clean <- data.frame(page_name = differences_df_clean, Indicator = "Only in df_similarity")
 
```

This analysis revealed 56 accounts that paid for FB ads but Crowdtangle could not identify them. These accounts can be found in df_differences_df_clean.

#Combine original df with data about FB ads.

```{r}
#Merge datasets 
df_ads_combinedT <- left_join(df_LATINMERGE, df_ads_clean, by = "page_name", na_matches = "never")
```

### Distribution

```{r}
df_terms$ad_creative_bodies = stri_trans_general(str = df_terms$ad_creative_bodies, id = "Latin-ASCII")                                             #removing accents
df_terms$ad_creative_bodies <- tolower(df_terms$ad_creative_bodies)  #lower case


################################
#Tokenization and identification
#First, we need to check whether each element in the body variable contains any of the municipality names.
ads_with_muni <- df_terms %>% 
          filter(
          str_detect(ad_creative_bodies, paste(muni_clean$name_muni, collapse = "|"), negate = F)
          )   

#This procedure identified 14,044 ads.
```

```{r}
ads <- str_extract_all(
  df_terms$ad_creative_bodies, 
  paste(muni_clean$name_muni, collapse = "|"), 
  simplify = FALSE)

ads_list <- ads %>% 
  unlist() %>%  
  as.data.frame()
  colnames(ads_list) <- "name_muni"  
ads_muni_mentioned <- ads_list %>%  
  group_by(name_muni) %>% 
  count()

#Adding the number of mentions to the datalist 
muni4 <- left_join(muni_clean, ads_muni_mentioned, by = "name_muni", copy = FALSE, keep = FALSE)

muni4$n <- muni4$n %>% replace_na(0)

####################################################
#############  REPLACE AMBIGUOUS NAMES #############

muni4 <- muni4 %>%
  mutate(n = ifelse(name_muni == "bandeira", 2, n))  %>% 
  mutate(n = ifelse(name_muni == "conquista", 0, n)) %>% 
  mutate(n = ifelse(name_muni == "divino", 8, n))    %>% 
  mutate(n = ifelse(name_muni == "extrema", 14, n))   %>%
  mutate(n = ifelse(name_muni == "liberdade", 8, n))  %>%
  mutate(n = ifelse(name_muni == "luz", 6, n))        %>% 
  mutate(n = ifelse(name_muni == "machado", 29, n))   %>% 
  mutate(n = ifelse(name_muni == "passos", 95, n))   %>% 
  mutate(n = ifelse(name_muni == "paiva", 2, n))      %>% 
  mutate(n = ifelse(name_muni == "campanha", 10, n))   %>% 
  mutate(n = ifelse(name_muni == "cristina", 3, n))   %>% 
  mutate(n = ifelse(name_muni == "goncalves", 5, n))  %>% 
  mutate(n = ifelse(name_muni == "pimenta", 4, n))


# bandeira  =  2
# conquista =  0
# divino    =  8
# extrema   =  14
# liberdade =  8
# luz       =  6
# machado   =  29
# passos    =  95
# paiva     =  2
# campanha  =  10
# cristina  =  3
# goncalves =  5
# pimenta   =  4

```

```{r, results='hide', message=FALSE, warning=FALSE}
#UNIQUE MENTIONS PER CANDIDATE
#Exclude ambiguous names 
ambiguous_names <- c("campanha", "cristina", "bandeira", "conquista", "divino", "extrema", "goncalves", "liberdade", "luz", "machado", "passos", "paiva", "pimenta")
filtered_muni_names <- muni_clean$name_muni[!(muni_clean$name_muni %in% ambiguous_names)]

###############################
###############################
# Count mentions of filtered_muni_names in the body column
muni_mentions_analysis_ads <-  ads_with_muni %>%
  mutate(mentioned_cities = str_extract_all(ad_creative_bodies, paste(filtered_muni_names, collapse = "|"))) %>%
  unnest(mentioned_cities) %>%
  group_by(page_name, mentioned_cities) %>%
  summarise(
    total_mentions = n(),
    unique_mentions = 1,
    cities_mentioned = paste(mentioned_cities, collapse = ", ")
  ) %>%
  group_by(page_name) %>%
  summarise(
    total_mentions = sum(total_mentions),        #Total count of city mentions for each candidate
    unique_mentions = n(),                       #Number of unique cities mentioned for each candidate
    cities_mentioned = list(unique(mentioned_cities))   #A list of city names mentioned by each candidate
  )

###############################
#### Adding ambiguous names ###
###############################
muni_mentions_analysis_ads_combined <- full_join(muni_mentions_analysis_ads, muni_ambiguous_analysis_ads, by = c("page_name" = "page_name.y")) %>%
  mutate(
    total_mentions = ifelse(is.na(total_mentions.y), total_mentions, total_mentions + total_mentions.y),
    unique_mentions = ifelse(is.na(unique_mentions.y), unique_mentions, unique_mentions + unique_mentions.y),
    cities_mentioned = map2(cities_mentioned, cities_mentioned.y, union)
  ) %>%
  select(page_name, total_mentions, unique_mentions, cities_mentioned)
```

**What is the average number of unique city mentions by a candidate?**

```{r}

mean(muni_mentions_analysis_ads_combined$unique_mentions, na.rm = TRUE)

median(muni_mentions_analysis_ads_combined$unique_mentions, na.rm = TRUE)

sd(muni_mentions_analysis_ads_combined$unique_mentions, na.rm = TRUE)
```

**What is the average number of city mentions by a candidate?**

```{r}
mean(muni_mentions_analysis_ads_combined$total_mentions, na.rm = TRUE)

median(muni_mentions_analysis_ads_combined$total_mentions, na.rm = TRUE)

sd(muni_mentions_analysis_ads_combined$total_mentions, na.rm = TRUE)
```

**Adding Census Data**

```{r}
IBGE_ads <- left_join(muni4, MGMunicipalities_Clean, by = "name_muni", copy = T, keep = FALSE)
IBGE_ads <- replace(IBGE_ads, is.na(IBGE_ads), 0)
```

**How many municipalities were mentioned less than ten times?**

```{r}
sum(IBGE_ads$n <10, na.rm=TRUE)
```

### Correlations

```{r}
CorrelationIDHM_ads <- cor.test(IBGE_ads$n, IBGE_ads$IDHM, 
                    method = "pearson")

CorrelationPopulation_ads <- cor.test(IBGE_ads$n, IBGE_ads$Population_2021, 
                    method = "pearson")

CorrelationPIB_ads <- cor.test(IBGE_ads$n, IBGE_ads$PIB_per_capita, 
                           method = "pearson")


CorrelationPopulation_ads
CorrelationIDHM_ads
CorrelationPIB_ads
```

```{r}
hist(IBGE_ads$n, 
     breaks = 100,  
     col = "skyblue",
     border = "white",  
     ylab = "",
     xlab = "",
     main = "Histogram of Mentions"  
)
```

```{r}
IBGE_ads_log <- IBGE_ads

#Log transformation of number of mentions
IBGE_ads_log$n <- log(IBGE_ads_log$n + 1)

hist(IBGE_ads_log$n, 
     col = "skyblue",
     border = "white",
     xlab = "",  
     main = "Histogram of Mentions"  
)
```

```{r}
Model_ads_Geo <- lm(n ~ Population_2021 + IDHM + PIB_per_capita,
                       data = IBGE_ads_log) 
omnibus_ads_geo <- Anova(Model_ads_Geo, type = "III")
omnibus_ads_geo
```

```{r}
# Check for multicollinearity using vif()
vif_ads_geo <- vif(Model_ads_Geo)
print(vif_ads_geo)
summary(Model_ads_Geo)
```

```{r}
IBGE_ads_clean <- IBGE_ads %>% 
  filter(!is.na(n))

BV_ads <- ggplot()+
  geom_jitter(data=IBGE_ads_log, aes(x = n, y = Population_2021, text=name_muni)) + 
  labs(title = "Relationship between mentions in ads and population (estimated for 2021)", x = "Mentions in ads", y = "population")+
  guides(fill = guide_colourbar(title = "Mentions")) 
  
InteractivePopulation_ads <- plotly::ggplotly(BV_ads)
InteractivePopulation_ads
```

```{r}
IBGE_ads_TEST <- st_as_sf(IBGE_ads, wkt = "geom")

# Ploting an interactive choropleth map
Map_ads_TEST <- ggplot(data=IBGE_ads_TEST) +
  geom_sf(aes(fill=n, text=name_muni, geometry=geom), color= NA, size=.15) + 
    labs(title="2022 Election: municipalities mentioned", size=10) +
    guides(fill = guide_colourbar(title = "Mentions")) +
    theme_minimal() +
    theme(axis.line = element_blank(), axis.text = element_blank(),
        axis.ticks = element_blank(), axis.title = element_blank(),
        panel.grid = element_blank()) +
  scale_fill_viridis_c()

InteractiveMap_ads <- ggplotly(Map_ads_TEST) %>% 
  layout(title = list(text = paste0("<B>2022 Election: municipalities mentioned in ads</B>")))

InteractiveMap_ads
```

```{r}
# Black and white color scale
custom_colors <- colorRampPalette(c("#D3D3D3", "black"))(n = 100)

# Choropleth map
Map_ads_black <- ggplot(data=IBGE_ads) +
  geom_sf(aes(fill=n, text=Name, geometry=geom), color= NA, size=.15) + 
    labs(title="2022 Election: municipalities mentioned", size=10) +
  guides(fill = guide_colourbar(title = "Mentions")) +
  theme_minimal() +
  theme(
    axis.line = element_blank(), axis.text = element_blank(),
    axis.ticks = element_blank(), axis.title = element_blank(),
    panel.grid = element_blank()
  ) +
  scale_fill_gradientn(
    colours = custom_colors
  )

InteractiveAdsMapBlack <- ggplotly(Map_ads_black) %>%
  layout(title = list(text = paste0("<B>2022 Election: municipalities mentioned</B>")))

InteractiveAdsMapBlack
```

